---
title: "P8105 Homework 6"
author: "Siyue Gao"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	fig.height = 6,
	out.width = "90%",
	dpi = 200
)
```


```{r}
library(tidyverse)
```


```{r}
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

### Data Cleaning

Import the data.

```{r}
homicide = read_csv("data/homicide-data.csv")
```

Create a `city_state` variable and a `status` binary variable indicating whether the homicide is solved. Omit cities without victim race reported and those with data entry mistake.

```{r}
homicide = homicide %>% 
  mutate(
    state = str_to_upper(state),
    city_state = str_c(city, ", ", state),
    status = case_when(
      disposition == "Closed by arrest"      ~ "resolved",
      disposition == "Closed without arrest" ~ "unresolved",
      disposition == "Open/No arrest"        ~ "unresolved",
      TRUE                                   ~ ""
    )
  ) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
```

Limit the analysis to those whom `victim_race` is `white` or `black`. Change `victim_age` into numeric.

```{r}
homicide_sub = homicide %>% 
  filter(victim_race %in% c("Black", "White")) %>% 
  mutate(victim_age = as.numeric(victim_age))
```

### Logistic Regression

```{r}
fit = 
  homicide_sub %>% 
  filter(city_state == "Baltimore, MD") %>% 
  mutate(
    status = fct_relevel(status, "unresolved")
  ) %>% 
  glm(status ~ victim_age + victim_sex + victim_race, data = ., family = "binomial")
```

Use `broom::tidy()` to extract the results of logistic regression.

```{r}
fit %>% 
  broom::tidy() %>% 
  knitr::kable(
    col.names = c("Term", "Estimated", "Std.Error", "Statistic", "p-value")    
  )

confint(fit) %>% 
  knitr::kable(digits = 3)
```

To get the estimate and confidencee interval of the adjusted **odds ratio**, we need to exponentiate the coefficient and the confidence interval.

```{r}
exp(cbind(coef(fit), confint(fit))) %>% 
  knitr::kable(digits = 3)
```

